\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=0.2in}

\begin{document}

\begin{center}
    \textbf{\huge{Amschel Kariuki}}\\
    Nairobi, Kenya \\
    \href{mailto:art68401@gmail.com}{art68401@gmail.com} \\
    +254797168636 \\
    \vspace{0.5cm}
\end{center}

\section*{Professional Summary}
Experienced React Native developer with over 4 years of experience in building high-quality mobile applications for startups. Expertise in TypeScript and Node.js, with a strong background in scalable backend development using Node/Express and microservices architecture. Proficient in DevOps, AWS, and Microsoft Azure. Contributed to open source projects and incubated a startup at ICP Hub Kenya.

\section*{Skills}
\begin{itemize}
    \item \textbf{Languages:} TypeScript, JavaScript, Rust, Java
    \item \textbf{Technologies:} React, React Native, Expo, Tailwind CSS, Node.js, Express.js
    \item \textbf{DevOps:} Docker, Kubernetes, AWS (S3), Microsoft Azure
    \item \textbf{Blockchain:} ICP (Internet Computer Protocol)
\end{itemize}

\section*{Professional Experience}

\textbf{Mobile Developer} \hfill \textit{Tamu} \\
\textit{Nairobi, Kenya} \hfill \textit{[Year - Year]} \\
\begin{itemize}
    \item Developed a dating app using React Native.
    \item Implemented features, fixed bugs, and improved performance.
\end{itemize}

\textbf{Mobile Developer} \hfill \textit{NichLabs} \\
\textit{Nairobi, Kenya} \hfill \textit{[Year - Year]} \\
\begin{itemize}
    \item Built an app for professionals using React Native.
    \item Collaborated with cross-functional teams to define, design, and ship new features.
\end{itemize}

\textbf{Mobile Developer} \hfill \textit{Serenity} \\
\textit{Nairobi, Kenya} \hfill \textit{[Year - Year]} \\
\begin{itemize}
    \item Developed a mental health app using React Native.
    \item Worked on UI design, integration with backend services, and deployment.
\end{itemize}

\section*{Projects}

\textbf{Vinyl Player} \hfill \textit{[Year - Year]} \\
\begin{itemize}
    \item Developed a music app available on GitHub.
    \item Utilized React Native and integrated various music APIs.
\end{itemize}

\textbf{Veestream} \hfill \textit{[Year - Year]} \\
\begin{itemize}
    \item Built a server deployment and file storage solution using Microsoft Azure.
    \item Demonstrated server management and DevOps skills.
\end{itemize}

\textbf{Quick Mongo Seed} \hfill \textit{[Year - Year]} \\
\begin{itemize}
    \item Developed an npm library for seeding MongoDB databases.
    \item Extensive use of TypeScript and Node.js.
\end{itemize}

\section*{Education}

\textbf{Computer Science} \hfill \textit{Kenyatta University} \\
\textit{Nairobi, Kenya} \hfill \textit{[Year - Year (Not graduated)]}

\section*{Open Source Contributions}
\begin{itemize}
    \item Contributed to various open source React Native projects.
\end{itemize}

\section*{Startup Experience}
\textbf{Incubated Startup} \hfill \textit{ICP Hub Kenya} \\
\begin{itemize}
    \item Worked on a token launch platform on ICP.
\end{itemize}

\end{document}
