% Resume in Latex
% Author : Your Name
% License : MIT

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item
  \textbf{#1}\hfill #2 \\
  \textit{\small#3}\hfill \textit{\small #4}
  \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/amschel99}{AMSCHEL KARIUKI}} & Email : \href{mailto:kariukiamschel9@gmail.com}{kariukiamschel9@gmail.com}\\
  \href{https://github.com/amschel99}{https://github.com/amschel99} & Mobile : +254797168636 \\
  \href{https://www.linkedin.com/in/amschel-kariuki-a83b9a230/}{https://www.linkedin.com/in/amschel-kariuki-a83b9a230/} & Website: \href{https://amschel-tech.vercel.app}{https://amschel-tech.vercel.app} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary Statement}
I am a results-driven Software Developer with a keen interest in blockchain and cryptography. Currently, I focus on implementing various blockchain protocols, such as digital signature schemes, funding algorithms, asset tokenization, DAOs, and token economics. My contributions span open source blockchain protocols and projects, including the Internet Computer and Bitcoin Layer 2s. I have extensive experience in web2 development with TypeScript, React Native, and Node.js, building products for diverse clients. Additionally, I am an author working on a book, "The Nitty Gritty of Blockchain and Cryptocurrency Engineering," which delves into blockchain concepts to provide a solid foundation in cryptocurrency engineering.

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{React Native Mobile Developer}{Particle Ventures}
{January 2022 - September 2022}
{\begin{itemize}[leftmargin=*]
  \item Developed the Tamu mobile application, a dynamic social networking app for iOS and Android.
  \item Collaborated with cross-functional teams including UI/UX designers and backend developers.
  \item Contributed to the end-to-end development process from design to deployment.
\end{itemize}}

\resumeSubheading
{CTO, Software Engineer}{Nichlabs}
{March 2023 - October 2023}
{\begin{itemize}[leftmargin=*]
  \item Spearheaded platform development, collaborating with design teams to establish design strategies.
  \item Built backend infrastructure using GraphQL and Node.js, ensuring robust application foundations.
  \item Integrated frontend and backend components seamlessly, enhancing user experience.
  \item Implemented DevOps practices for server availability and continuous operation.
\end{itemize}}

\resumeSubheading
{Software Developer}{Serenity}
{December 2023 - February 2024}
{\begin{itemize}[leftmargin=*]
  \item Developed Serenity, an app to assist recovering addicts in their recovery journey.
  \item Implemented the Sober Token, a utility token for app users based on their usage.
  \item Contributed to the technical development and tokenomics of Sober Token.
\end{itemize}}

\resumeSubheading
{Decentralized Funding DAO Developer}{Olympus Accelerator (ICP Hub Kenya)}
{January 2024 - June 2024}
{\begin{itemize}[leftmargin=*]
  \item Developed a decentralized funding DAO for high-growth web3 startups.
  \item Incubated and supported under the Olympus Accelerator platform at ICP Hub Kenya.
  \item Facilitated funding mechanisms and governance structures leveraging blockchain technologies.
\end{itemize}}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Science in Computer Science}{Kenyatta University}
{2018-2022}{}
\resumeItemListStart
\resumeItem{Relevant Coursework}
{Data Structures and Algorithms, Software Engineering, Database Management Systems, Operating Systems, Web Development, Mobile App Development, Computer Networks, Artificial Intelligence, Human-Computer Interaction}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{Programming Languages}
{Rust, Node.js, TypeScript, JavaScript}
\resumeItem{Frameworks and Libraries}
{React Native, React.js, Langchain}
\resumeItem{Blockchain Technologies}
{ICP Blockchain, Bitcoin Layer 2s}
\resumeItem{Tools and Platforms}
{Nginx, Microsoft Azure}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{Rust ICP Cycles Library}
{Developed a Rust library to programmatically convert ICP tokens into cycles.}
\resumeItem{ICRC2 Token Platform}
{Built a platform to create ICRC2 tokens on the fly without coding.}
\resumeItem{Decentralized Funding DAO}
{Created a DAO for decentralized funding of high-growth web3 startups.}
\resumeItem{lsig}
{Authored "lsig," a Lamport signatures implementation in Rust.}
\resumeItem{Video Processing App}
{Developed a video processing app using Node.js, React Native, and ffmpeg.}
\resumeItem{Asset Tokenization System}
{Implemented an asset tokenization system using ICP, Rust CDK. Currently proprietary  }
\resumeItem{File Storage and Management API}
{Created a file storage and management API using Microsoft Azure and Node.js. Monetized at Rapid API for 3 months. (\href{https://github.com/amschel99/veestream}{https://github.com/amschel99/veestream})}
\resumeItem{Database Seeding Library}
{Developed a database seeding library using TypeScript for software testing. (\href{https://github.com/amschel99/quick-mongo-seed}{https://github.com/amschel99/quick-mongo-seed})}

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
